---
title: "p8105_hw1_ryw2109"
author: "Rita Wang"
date: "2024-09-22"
output: html_document
---
```{r librarys_used}
library(palmerpenguins)
library(tidyverse)
```

```{r HW1Q1_part1, eval = FALSE}
data("penguins", package = "palmerpenguins")

  # the data in this dataset, including names / values of important variables
    # provides the variable names and 
names(penguins)
    # the first 10 rows of the dataset
unique(penguins)

  # the number of rows in the dataset
nrow(penguins)

  # the number of columns in the dataset
ncol(penguins)

  # the mean flipper length with the removal of null values
mean(penguins$flipper_length_mm, na.rm = TRUE)
```

There is a total of `r nrow(penguins)` rows and `r ncol(penguins)` columns where there exists null values such as NA. The following are the variable names of the dataset:

`r names(penguins)`

There is an average flipper length of `r mean(penguins$flipper_length_mm, na.rm = TRUE)` mm.

```{r HW1Q1_part2}
  # Make a scatterplot of flipper_length_mm (y) vs bill_length_mm (x); color points using the species variable (adding color = ... inside of aes in your ggplot code should help).
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()

  # Export your first scatterplot in your project directory using ggsave.
ggsave ("Bill Length VS Flipper Length.pdf")
```


```{r HW1Q2_part1}
hw_df = tibble(
    # a random sample of size 10 from a standard Normal distribution
  random_sample = rnorm(10),
  
    # a logical vector indicating whether elements of the sample are greater than 0
  logical_vector = random_sample > 0,
  
    # a character vector of length 10
  character_vector = c("Hello", "this", "is", "probably", "a", "charcter", "vector", "of", "length", "10"),
  
    # a factor vector of length 10, with 3 different factor “levels”
  factor_vector = factor(c("Rainy", "Sunny", "Cloudy", "Rainy", "Rainy", "Sunny", "Sunny", "Cloudy", "Cloudy", "Sunny"))
)

hw_df

  # Mean of each variable in the dataframe
random_sample_mean <- hw_df %>% pull(random_sample) %>% mean(na.rm = TRUE)
  random_sample_mean
logical_vector_mean <- hw_df %>% pull(logical_vector) %>% mean(na.rm = TRUE)
  logical_vector_mean
character_vector_mean <- hw_df %>% pull(character_vector) %>% mean(na.rm = TRUE)
  character_vector_mean
factor_vector_mean <- hw_df %>% pull(factor_vector) %>% mean(na.rm = TRUE)
  factor_vector_mean
```

The mean of the random sample of size 10 from a standard normal distribution is `r random_sample_mean` where this value indicates the average value of the following 10 random numeric values:

`r random_sample`

The mean of the logical vector indicating whether elements of the sample are greater than 0 is `r logical_vector_mean`. This value does not have any meaning as it is only the mean of the False (0) and True (1) contained in this vectors.

The mean of the character vector of length 10 is `r character_vector_mean`. There is no mean computed as the character vector does not contain integers.

The mean of the factor vector of length 10, with 3 different factor “levels” `r factor_vector_mean`. There is no mean computed as the factor vector does not contain integers as well.

```{r HW1Q2_part2}

```

